Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-01 draft.tex
working on the unit

Consider now a fixed open set $V \subset \RR^n$.
Then the $L_\infty$ map $f: \fg \rightsquigarrow \fh$ induces canonically an $L_\infty$ map 
\[
\tilde{f}: \Omega^*_c(V) \otimes \fg \to \Omega^*_c(V) \otimes \fh
\]
by base change along the map $k \to \Omega^*_c(V)$ of dg commutative algebras,
as the compactly supported de Rham forms form a dg commutative algebra under wedge product.
In consequence, we see that $\Omega^*_c(V) \otimes \fg$ acts on $\Omega^*_c(V) \otimes \fh$ and hence equips it with the structure of an $L_\infty$ module over $\Omega^*_c(V) \otimes \fg$.
We denote this module as
\[
(\Omega^*_c(V) \otimes \fh)_f
\]
to emphasize the dependence on the original map~$f$.
In this action, the wedge product of forms intertwines with the $L_\infty$ structure on $\fg$ in a very simple way: 
they simply happen side by side, but do not affect each other.

@@

%We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.
%
%First note that compactly supported form embeds in all forms, therefore we can apply 
%any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
%to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
%\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
%\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
%  \\
% (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
%\end{equation} induced by this embedding  in all forms followed by evaluating on a function.
%
%Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
%$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
%We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
%\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
%B(\emptyset) \ar[r] & B(U)  } 
% \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
% $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
% of the factorization structure of 
% the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
% The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
% \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
% $B$. We therefore obtain a canonical splitting of factorization algebras 
% \begin{equation}\label{eq:splittingbyaugm}
%   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
% \end{equation}
%given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
%a natural grading on it.
% 
% 
% 
%
%We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
%\begin{multline}\label{eq:defevforconnected}
% \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
% \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
% \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
% \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
% \right) \\
% \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
% B(W)
%\end{multline}
%where $\mathbf{f}$ is the factorization algebra morphism  we are given.
%In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
%we have 
%\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
%
%
%
%
%
%
%
%We extend this construction  to any 
% open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
% More precisely, 
%  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
%of its connected components. Using, the natural isomorphisms of complexes 
%\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
%\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
%\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
%\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
%$\bigotimes_{i\in I} B(U_i) 
%\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
% (natural) decomposition 
%\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
% \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
% \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
% \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
%\end{multline}
%and we can therefore define 
%\begin{multline}\label{eq:defineevf}
% \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
% \\ \stackrel{\simeq}\longrightarrow  
%\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
% \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
% \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
% \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
%\end{multline}
%where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
%and~\eqref{eq:defevforconnected}.
%\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
%things to do (like completion) for non-finitely dimensional Lie algebras}
%\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
%out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}
%
%
%\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
%the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
%is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
%$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
% \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
%\end{equation}
%where $J$ runs through all the (possibly empty) subsets of $I$.  Precisely, the $J$-piece is
%\begin{multline*}
%{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
%\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
%\overline{\clies (\fg\otimes \Omega (U_j), B(U_j))  }\right) \\ \cong 
%\overline{\clies (\fg\otimes \Omega (\coprod\limits_{j\in_J}U_j), B(\coprod\limits_{j\in_J}U_j))  }.
%\end{multline*}
%We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
%\emph{with support $\coprod\limits_{j\in J} U_j$}.   
%Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
%${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
%\end{rmk}
%In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
%$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
%have the following formula generalizing the one for connected open  subsets:
%\begin{equation} \ev_f^U(\varphi\otimes X)= \sum_{J\subset I} \mu_B\left(\mathbf{f}\Big(\bigotimes\limits_{i\in I\setminus J} 
%X_i\Big)\otimes  \varphi^{(J)}\Big(\bigotimes\limits_{j\in J} 
%X_j\Big)\right) \end{equation}
%where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
%is the  structure map of $B$.
%

@@

\subsection{End of the proof}

Combining the result of the last two sections we obtain immediately the following factorization algebra model for our main theorem:
\begin{thm}\label{thm:centralizerfactorization}
Let $k$ be $\RR$ or $\CC$, and assume $\mathbf{f}:  \UU_n \fg \to B$ is a map of augmented factorization algebras. 
Then, the centralizer ${\frak Z}(\mathbf{f})$ is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), B(U))
\]
to each open set $U \subset \RR^n$. 
\end{thm}
\begin{proof}
 In section~\ref{SS:constuctionthetaf}, we have constructed a factorization algebra map 
 $\theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})$. Proposition~\ref{L:canonicaltocenterisquis} 
 states that this map is an equivalence he Chevalley-Eilenberg factorization algebra cochains and the factorization algebra center of $f$ as claimed.
\end{proof}

By Lurie's equivalence (Theorem~\ref{T:En=Fac}) between the $\infty$-categories of $E_n$-algebras and locally constant factorization algebras 
over $\RR^n$ (and the last part of lemma~\ref{L:thetaquisondisk}),
the main theorem~\ref{thm: centralizer} follows from its factorization algebra counterpart~\ref{thm:centralizerfactorization}, 
that is from Theorem~\ref{thm:centerfactorization}. This proves the theorem over $k=\RR$ (or $\CC$).

Corollary~\ref{cor:centerfactorization}  is a consequence of theorem~\ref{thm:centralizerfactorization} obtained from applyting the universal 
$E_n$-enveloping algebra functor to a (homotopy) Lie algebra homomorphism.

\greg{Add a base change result to get the result over Q ? Add the center structure. I.E. write and check (!) that we can write a structure of $E_1$algebra in factorization algebra describing the higher $E_{n+1}$-structure for $f=id$}

\owen{Commented out here is a discussion of centers. We may want to resurrect it but it doesn't seem essential to the main results.}

>>>>

Consider now a fixed open set $V \subset \RR^n$.
Then the $L_\infty$ map $f: \fg \rightsquigarrow \fh$ induces canonically an $L_\infty$ map 
\[
\tilde{f}: \Omega^*_c(V) \otimes \fg \rightsquigarrow \Omega^*_c(V) \otimes \fh
\]
by base change along the map $k \to \Omega^*_c(V)$ of dg commutative algebras,
as the compactly supported de Rham forms form a dg commutative algebra under wedge product.
In consequence, we see that $\Omega^*_c(V) \otimes \fg$ acts on $\Omega^*_c(V) \otimes \fh$ and hence equips it with the structure of an $L_\infty$ module over $\Omega^*_c(V) \otimes \fg$.
We denote this module as
\[
(\Omega^*_c(V) \otimes \fh)_f
\]
to emphasize the dependence on the original map~$f$.
In this action, the wedge product of forms intertwines with the $L_\infty$ structure on $\fg$ in a very simple way: 
they simply happen side by side, but do not affect each other.

@@

\greg{
We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.\\
First note that compactly supported form embeds in all forms, therefore we can apply 
any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
  \\
 (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
\end{equation} induced by this embedding  in all forms followed by evaluating on a function.\\
Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
B(\emptyset) \ar[r] & B(U)  } 
 \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
 $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
 of the factorization structure of 
 the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
 The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
 \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
 $B$. We therefore obtain a canonical splitting of factorization algebras 
 \begin{equation}\label{eq:splittingbyaugm}
   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
 \end{equation}
given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
a natural grading on it.\\
We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
\begin{multline}\label{eq:defevforconnected}
 \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
 \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
 \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
 \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
 \right) \\
 \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
 B(W)
\end{multline}
where $\mathbf{f}$ is the factorization algebra morphism  we are given.
In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
we have 
\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
We extend this construction  to any 
 open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
 More precisely, 
  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
of its connected components. Using, the natural isomorphisms of complexes 
\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
$\bigotimes_{i\in I} B(U_i) 
\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
 (natural) decomposition 
\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
 \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
 \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
 \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
 \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
\end{multline}
and we can therefore define 
\begin{multline}\label{eq:defineevf}
 \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
 \\ \stackrel{\simeq}\longrightarrow  
\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
 \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
 \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
 \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
\end{multline}
where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
and~\eqref{eq:defevforconnected}.
\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
things to do (like completion) for non-finitely dimensional Lie algebras}
\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}\\
\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
 \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
 \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
\end{equation}
where $J$ runs through all the (possibly empty) subsets of $I$.  Precisely, the $J$-piece is
\begin{multline*}
{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
\overline{\clies (\fg\otimes \Omega (U_j), B(U_j))  }\right) \\ \cong 
\overline{\clies (\fg\otimes \Omega (\coprod\limits_{j\in_J}U_j), B(\coprod\limits_{j\in_J}U_j))  }.
\end{multline*}
We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
\emph{with support $\coprod\limits_{j\in J} U_j$}.   
Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
\end{rmk}
In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
have the following formula generalizing the one for connected open  subsets:
\begin{equation} \ev_f^U(\varphi\otimes X)= \sum_{J\subset I} \mu_B\left(\mathbf{f}\Big(\bigotimes\limits_{i\in I\setminus J} 
X_i\Big)\otimes  \varphi^{(J)}\Big(\bigotimes\limits_{j\in J} 
X_j\Big)\right) \end{equation}
where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
is the  structure map of $B$.
}

@@
